Assessment and Optimization of Nowcast Measures for Trend Detection

### 2024-01-13 paper.tex
Update on Overleaf.

\begin{tabularx}{\textwidth}{c l l l}
     & Indicator & Weighted 1 & Weighted 2 \\
     Verrauschte Daten & & & \\
     Konzentration in Q1/Q3, aber viel an Entscheidungsgrenzen, kein Noise & & & \\
     $\ydiff_t = \xdiff_t$ und $\ydiff_t \sim N(0, 1)$ & & & \\

>>>>

\begin{tabularx}{\textwidth}{c l l l}
     & Indicator & Weighted 1 & Weighted 2 \\
     \includegraphics{plots/simulation_com} & & & \\
     Konzentration in Q1/Q3, aber viel an Entscheidungsgrenzen, kein Noise & & & \\
     $\ydiff_t = \xdiff_t$ und $\ydiff_t \sim N(0, 1)$ & & & \\
